Paper 1

### 2022-05-28 scripts/Paper 1.Rmd
add monthly avg

```{r setup, include=FALSE}
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(dplyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)
library(htmltools)

@@

input$jday <-yday(input$Timestamp) # add jday
input$Year <- year(input$Timestamp) # extract year
input$Year <- as.factor(input$Year) # convert year from integer to factor
input$month <- month(as.POSIXct(input$Timestamp)) # extract month
```

@@

rainfall <- rbind(rainfall_L, rainfall.SP)

@@

```{r create rainfall summary}
rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "season"), summarise,
                                       seasonal.sum = sum(Precip, na.rm = TRUE))

rainfall.summary %>% 
  ggplot(., aes(x = season, y = seasonal.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

```
```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("Year", "season", "jday"), summarise,
                                       seasonal.sum = cumsum(NEE_LT.gC))

@@

@@

```{r timeseries analysis}
library(forecast)
```

>>>>

```{r setup, include=FALSE}
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(dplyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)
library(htmltools)
library(ggpubr)
library(rstatix)
library(broom)

@@

input$jday <-yday(input$Timestamp) # add jday
input$Year <- year(input$Timestamp) # extract year
input$Year <- as.factor(input$Year) # convert year from integer to factor
input$month <- month(as.POSIXct(input$Timestamp)) # extract month
input$month <- as.factor(input$month)
```

@@

rainfall <- rbind(rainfall_L, rainfall.SP)
rainfall$month <- as.factor(rainfall$month)

@@

```{r create rainfall summary}
rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "month"), summarise,
                                       monthly.sum = sum(Precip, na.rm = TRUE))

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_point(aes(color = Year, size = 2)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("month", "Year"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

@@

```{r timeseries analysis}
tsData <- EuStockMarkets[, 1] # ts data
decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
plot (decomposedRes) # see plot below
stlRes <- stl(tsData, s.window = "periodic")

input.daily %>% anova_test(NEE_LT.gC~Precip+season)

rainfall$TS <- as.Date(with(rainfall, paste(Year, month, jday,sep="-")), "%Y-%m-%d")

TSData <- rainfall[, 1] # ts data
decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
plot (decomposedRes) # see plot below
stlRes <- stl(tsData, s.window = "periodic")
```
